An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-19 draft.tex
Rewrites abstract, reducing it

\begin{abstract} 
Multi-population based methods have been used extensively in
recent years to improve the performance of nature-inspired optimization
algorithms. These methods are parallel and asynchronous by nature and researchers
leverage this to scale implementations 
applying distributed, multi-threaded, parallel, and cloud-based computing. 
% scale implementations with ... implementations. Please rephrase - JJ 
% done - Mario
However, the design  of these cloud-native,  
distributed, multi-population algorithms is not a trivial task. Designers need
to adapt their solutions 
% design of algorithms is not trivial... designer need to adapt the algorithms... Maybe rephrase to avoid repetition - JJ 
to leverage
the scalability, elasticity, fault-tolerance, reproducibility, and
cost-effectiveness of cloud systems while conserving the intended functionality.
% I am removing the native part above, because is also very repetetive - Mario 
% Something about "this is the problem we want to address... " to link the previous sentence with this one - JJ 
Furthermore, currently, there are no
cloud-native solutions that support basic algorithm design practices that can make
multi-population methods more efficient: having multiple search strategies, and
varying the number and size of subpopulations. We address these problems in this work,
by presenting the design and implementation of a cloud-native 
container-based % again maybe it's better cloud-native instead of reactive - JJ
application for the execution of ensemble multi-population algorithms. Researchers can
use the application to execute multiple experiments, both locally or in a cloud
environment, and deploy experiments by specifying the infrastructure as part of
an experiment definition so that results are easily reproducible.
% A sentence on how this implementation is better than the state of the art - JJ 
% Added a comment above - Mario, 
% But maybe we need to say it again? - Mario
% For instance "Generally the current implementations include a single algorithm, which is bad because... " - JJ 
% Also "Current implementations are more or less functional equivalent 
%to parallel, including the fact that they run copies of the same, parametrized, algorithm... 
% If this is too long, maybe just some reference about 
%"current implementation do not leverage the fact that (you can use different algorithms,
% and differently parametrized...) and then qualify this in the introduction - JJ
State of the art approaches use a single-algorithm implementation, and this might
not be the best solution. We compared the speedup, execution time, and the number
of evaluations between a single and an ensemble approach by using Genetic Algorithms (GAs)
and Particle Swarm Optimization (PSO) algorithms against a benchmark for the optimization
of continuous functions. Experiments show that the framework allows the ensemble 
to outperform single-algorithm versions.  
% We also run experiments to see the effect of population size for seveal problem sizes  
% Against NUMBER OF WORKERS (this concept is not mentioned yet)
% We can add something like:      
Moreover, we evaluated the effect other design parameters had on the
performance, in particular, the number and the size of populations concerning
the problem size. The architecture and the implemented platform is an excellent
alternative for locally or in the cloud, thus proving that cloud-native
bioinspired algorithms perform better in their "natural" environment than other
kinds of algorithms.
\end{abstract}

@@

\section{State of the Art} 
\label{soa}
Hadoop 
    Comparasion \cite{ferrucci2018using}
    Hadoop\cite{fazenda2012} 
    FlexGP \cite{FlexGP}, 
    elephant56 \cite{salza2016elephant56},

>>>>

\begin{abstract} 
Splitting a population into multiple instances is a technique that has been used extensively in
recent years to improve the performance of nature-inspired optimization
algorithms. Work on several populations can be done in parallel, and
also asynchronously, which can be leveraged to create scalable
implementations based on, among other methods, distributed, multi-threaded, parallel, and cloud-based computing. 
% I have rephrased all this. Please check it out - JJ
The design of these cloud-native, distributed, multi-population
algorithms is not a trivial task. Coming from monolithic
(single-instance) solutions, adaptations at several levels, from the
algorithmic to the functional, must be made to leverage
the scalability, elasticity, fault-tolerance, reproducibility, and
cost-effectiveness of cloud systems while, at the same time,
conserving the intended functionality. Instead of an evolutive
approach, in this paper we propose to create from scratch a
cloud-native optimization framework that is able to include multiple
algorithms and use few parameters to work. This solution goes beyond
current state of the art via a framework that is able to support
different algorithms at the same time, work asynchronously, and also
be easily deployable to any cloud platform. We evaluate the
performance and scalability of this solution, together with the effect
other design parameters had on the 
performance, in particular, the number and the size of populations
with respect to problem size. The architecture and the implemented platform is an excellent
alternative for locally or in the cloud, thus proving that cloud-native
bioinspired algorithms perform better in their "natural" environment than other
kinds of algorithms, and setting a new baseline for scaling and
performance in the cloud.
\end{abstract}

@@

\section{State of the Art} 
\label{soa}
Hadoop 
    Comparison \cite{ferrucci2018using}
    Hadoop\cite{fazenda2012} 
    FlexGP \cite{FlexGP}, 
    elephant56 \cite{salza2016elephant56},
